Forecasting the old-age dependency ratio to determine the best pension age

### 2020-05-04 PensionAge.Rmd
Removed hmd.R from repo

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
library(tidyverse)
library(demography)
#remotes::install_github("robjhyndman/addb")
library(addb)
library(patchwork)
library(kableExtra)
source("functions-v4.R")
source("hmd.R")
```

@@

# Get population data to 1 Jan 2019
aus.pop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
aus.pop <- extract.ages(aus.pop, ages = 0:100)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
library(tidyverse)
library(demography)
#remotes::install_github("robjhyndman/addb")
library(addb)
library(patchwork)
library(kableExtra)
source("functions-v4.R")
```

@@

# Get population data to 1 Jan 2019
source("hmd.R") # File only stores username and password
aus.pop <- hmd.pop(country = "AUS", username = username, password = password, 
                   label = "Australia")
aus.pop <- extract.ages(aus.pop, ages = 0:100)
